\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
section for inference part

By nature, the firing event is really fast and in order to
retrieve the connectivity from them, it is necessary to link a burst to a
couple of timesteps (ideally one).

The small decay for the fluorescent calcium indicator implies a signal
variation during a long time interval. Firing event are represented by strong
variations in the neuron activity. Therefore we apply a hard-tresholding
filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
threshold $\tau$ should be taken positive and non-close to zero to
respectivelty only keep rising edges and strong variations.

@@

Then we apply on the entire signal a non-linear filter based on the
current activity of the systems in order to favor the association measure inversely
proportional to the number of neurons firing together:
$ x^{t,w}_i  = (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} x_{t,d}^j}} $.
When too much neurons are firing together, i.e. in case of a network burst, it is almost
impossible to retrieve direct relationships: all neurons seem to be directly
connected to each other. By favoring the association measure when the activity is low,
we expect to retrieve a pair of neurons that are really directly connected together.
In concrete terms, as it can be verified on \textit{fig 1}, peak intensity may change in function
of the activity of all neurons but the number and the locations of peaks is not modified.

\subsection{Network inference through weighted average partial correlation
            coefficients}
\label{sec:inference}

@@

% Speak about why averaging
The quality of the signal filtering and network inference depends on
good hyper-parameter selection, which are themselves dependent on the properties
of the targeted network and measurement conditions, e.g. signal to noise ratio.
In order to improve robustness, a weighted average of partial correlation
matrices was estimated from the time series by varying the hard-threshold value
$\tau$ and the design of the low-pass filter (coefficients $(c_l^k)_{l=-3}^k$).

@@

>>>>

By nature, the firing event is really fast and in order to
retrieve the connectivity from them, it is necessary to link a burst to a
couple of timesteps (ideally one). The small decay for the fluorescent calcium indicator implies a signal
variation during a long time interval. Firing event are represented by strong
variations in the neuron activity. Therefore we apply a hard-tresholding
filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
threshold $\tau$ should be taken positive and non-close to zero to
respectivelty only keep rising edges and strong variations.

@@

Then we apply on the entire signal a non-linear filter based on the current
activity of the systems in order to favor the association measure inversely
proportional to the number of neurons firing together: $ x^{t,w}_i  =
(x^{t,d}_i + 1 )^{1 + \frac{1}{act_t}}$ where $act_t = \sum_{j} x_{t,d}^j$ is
the activity of all neurons at time $t$. When too much neurons are firing
together, i.e. in case of a network burst, it is almost impossible to retrieve
direct relationships: all neurons seem to be directly connected to each other.
By favoring the association measure when the activity is low, we expect to
retrieve a pair of neurons that are really directly connected together. In
concrete terms, as it can be verified on \textit{fig 1}, peak intensity may
change in function of the activity of all neurons but the number and the
locations of peaks is not modified.

\section{Network inference through weighted average partial correlation
            coefficients}
\label{sec:inference}

@@

% Speak about why averaging
The quality of the signal filtering and network inference depends on
good hyper-parameter selection, which are themselves dependent on the properties
of the targeted network and measurement conditions, e.g. signal to noise ratio.
In order to improve robustness, a weighted average of partial correlation
matrices was estimated from the time series by varying the hard-threshold value
$\tau$ and the design of the low-pass filter (mentionned in section \ref{sec:filter} and appendix \ref{app:optimized}).

@@

\section{An optimized version of the algorithm to win the challenge}
\label{app:optimized}

%% Talk about filters future and past
